---
title: "Motion clouds rivalry: Relative onset / Delay"
author: "Egor Ananyev"
date: "April 23, 2017"
output:
    html_document:
      toc: yes
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
library(lme4)
library(BayesFactor)
library(gridExtra)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
#db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcEcc_ct-tRelXbv'
subjs <- c(0:3)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
allDirs <- allDirs[grep(paste(expt,'_p',sep=''), allDirs)]
```

## Plot variables
```{r}
dodge <- position_dodge(width=0)
alpha <- .8
cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
xLabStat <- 'Static Stimulus Delay (s)'
xLabDyna <- 'Dynamic Stimulus Delay (s)'
yLab <- 'Proportion of Trials'
yLabSz <- 'Center/Stimulus Size'
yLabCS <- 'Proportion Center-Surround'
colLab <- 'Response\nType'
colLab2 <- 'Response Type' # for use in indiv plots where col label is along the bottom
```

## Plot functions
```{r, message=FALSE, warning=FALSE}
# theme for plotting:
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=margin(t=-.04, unit='in'),
            legend.background = element_rect(fill='transparent'),
            plot.title=element_text(face='bold'))
}
plotAve <- function(pss, subjStr='subj', xStr, grpStr='resp', 
                    xlab, ylab=yLab, collab=colLab, yStr='mn', seStr='se'){
    pss$yMin <- pss[,yStr] - pss[,seStr]
    pss$yMax <- pss[,yStr] + pss[,seStr]
    p <- ggplot(pss, aes_string(x=xStr, y=yStr, colour=grpStr, group=grpStr,
                            ymin='yMin', ymax='yMax')) +
        geom_point(position=dodge, size=1, alpha=alpha) + geom_line(position=dodge, alpha=alpha) +
        scale_x_continuous(breaks=c(0,.2,.4,.6,.8,1), labels=c('0','0.2','0.4','0.6','0.8','1')) +
        geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
        labs(x=xlab, y=ylab, colour=collab) +  ylim(0,1) + 
        guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
    p <- themefy(p)
}
plotIndiv <- function(pss, subjStr='subj', xStr, grpStr='resp', 
                    xlab, ylab=yLab, collab=colLab2, yStr='mn', seStr='se'){
    pss$yMin <- pss[,yStr] - pss[,seStr]
    pss$yMax <- pss[,yStr] + pss[,seStr]
    p <- ggplot(pss, aes_string(x=xStr, y=yStr, colour=grpStr, group=grpStr,
                            ymin='yMin', ymax='yMax')) + 
        facet_grid(paste('.~factor(', subjStr, ')', sep='')) +
        geom_point(position=dodge, size=1, alpha=alpha) + geom_line(position=dodge, alpha=alpha) +
        geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
        scale_x_continuous(breaks=c(0,.2,.4,.6,.8,1), labels=c('0','','','','','1'), limits=c(0,1))+
        scale_y_continuous(breaks=c(0,.25,.5,.75,1), labels=c('0','','0.5','','1'), limits=c(0,1)) +
        labs(x=xlab, y=ylab, colour=collab) + 
        guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
    p <- themefy(p)
}
```

## Summary functions
```{r}
# computes individual and group means and SDs; req's y to be the var of interest
sumFn <- function(ss, subjStr='subj', xStr, grpStr='resp'){
    sumSubj <- ddply(ss, c(subjStr, xStr, grpStr), summarise,
                     mnS=mean(y), se=sd(y)/sqrt(length(y))) #, .drop=F)
    # sumSubj$mnS[is.na(sumSubj$mnS)] <- 0
    sumGrp <- ddply(sumSubj, c(xStr, grpStr), summarise,
                  mn=mean(mnS), se=sd(mnS)/sqrt(length(mnS)))
    sumGrp$subj <- 'average'
    sumSubj <- rename(sumSubj, c(mnS='mn'))
    sumComb <- rbind(sumGrp, sumSubj)
    sumComb$se[is.na(sumComb$se)] <- 0
    sumComb
}
# computes the proportion of different levels of 'grpStr' -- here, response types
sumPFn <- function(ss, subjStr='subj', xStr, grpStr='resp'){
    sumSubj <- ddply(ss, c(subjStr, xStr, grpStr), summarise, nm = length(subj), .drop=F)
    sumGrp <- ddply(sumSubj, c(subjStr, xStr), summarise, tot=sum(nm))
    sumSubj <- merge(sumSubj, sumGrp, by=c(subjStr,xStr))
    sumSubj$pSubj <- with(sumSubj, nm/tot)
    sumGrp <- ddply(sumSubj, c(xStr, grpStr), summarise,
                  mn=mean(pSubj), se=sd(pSubj)/sqrt(length(subj)))
    sumSubj <- rename(sumSubj, c(pSubj='mn'))
    sumSubj$se <- 0
    sumGrp$subj <- 'average'
    sumComb <- rbind(sumGrp, sumSubj[,c(subjStr,xStr,grpStr,'mn','se')])
    sumComb$se[is.na(sumComb$se)] <- 0
    sumComb
}
```

## Loading the data
```{r}
colsOfInt <- c('participant','session','trialN', #info
               'trialT', 'tOffL', 'tOffR', 'BvL', 'BvR', #IVs
               'nf000','nf090','nf180','nf270','ringSz') #DVs
df <- data.frame()
for(curSess in allDirs){
    print(curSess)
    sessFn <- paste(condDir, curSess, '/', curSess, '.csv', sep='')
    if(file.exists(sessFn)){
        curDs <- read.csv(sessFn)
        df <- rbind(df, curDs[,colsOfInt])
    }
}
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df #[colsOfInt]
ds <- rename(ds, c(participant='subj', session='sess', tOffL='tDelayL', 
                   tOffR='tDelayR'))
ds$subj <- as.factor(ds$subj)
# Size conversions:
# ds$ringSzDeg <- round((ds$ringSz+32)/35,1)
# ds$ringSzP <- round(ds$ringSzDeg/max(ds$ringSzDeg),2)
ds$ringSzDeg <- (ds$ringSz+32)/35
ds$ringSzP <- ds$ringSzDeg/max(ds$ringSzDeg)
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSzP < 1] <- 1
# tDelaystat/dyna
ds$tDelayStat <- 0
ds$tDelayStat[ds$BvL==0.01] <- ds$tDelayL[ds$BvL==0.01]
ds$tDelayStat[ds$BvR==0.01] <- ds$tDelayR[ds$BvR==0.01]
ds$tDelayDyna <- 0
ds$tDelayDyna[ds$BvL==9.6] <- ds$tDelayL[ds$BvL==9.6]
ds$tDelayDyna[ds$BvR==9.6] <- ds$tDelayR[ds$BvR==9.6]
head(ds)
```

# Types of responses
```{r}
# noDir, fastDir, statDir, transparent
ds$stat <- 0
ds$stat[ds$nf270==1] <- 1
ds$dyna <- 0
ds$dyna[ds$nf180==1] <- 1
ds$patchy <- 0
ds$patchy[ds$nf090==1] <- 1
ds$transp <- 0
ds$transp[ds$nf000==1] <- 1
ds$resp[ds$stat==1] <- 'static'
ds$resp[ds$dyna==1] <- 'dynamic'
ds$resp[ds$patchy==1] <- 'patchy'
ds$resp[ds$transp==1] <- 'transparent'
ds$resp <- factor(ds$resp, levels = c('static','dynamic','patchy','transparent'))
head(ds)
```

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
sumSs <- sumPFn(ss, xStr='tDelayStat')
sumSsAve <- sumSs[sumSs$subj=='average',]
pStat <- plotAve(pss=sumSsAve, xStr='tDelayStat', xlab=xLabStat)
pStatIndiv <- plotIndiv(pss=sumSs, xStr='tDelayStat', xlab=xLabStat)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### stat dom ~ static delay
```{r}
summary(glmer(stat ~ tDelayStat + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(stat ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(stat ~ tDelayStat + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

### dyna dom ~ static delay
```{r}
summary(glmer(dyna ~ tDelayStat + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(dyna ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(dyna ~ tDelayStat + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

### patchy dom ~ static delay
```{r}
summary(glmer(patchy ~ tDelayStat + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(patchy ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(patchy ~ tDelayStat + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
sumSs <- sumPFn(ss, xStr='tDelayDyna')
sumSsAve <- sumSs[sumSs$subj=='average',]
pDyna <- plotAve(pss=sumSsAve, xStr='tDelayDyna', xlab=xLabDyna)
pDynaIndiv <- plotIndiv(pss=sumSs, xStr='tDelayDyna', xlab=xLabDyna)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### stat dom ~ dynamic delay
```{r}
summary(glmer(stat ~ tDelayDyna + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(stat ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(stat ~ tDelayDyna + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

### dyna dom ~ dynamic delay
```{r}
summary(glmer(dyna ~ tDelayDyna + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(dyna ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(dyna ~ tDelayDyna + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

### patchy dom ~ dynamic delay
```{r}
summary(glmer(patchy ~ tDelayDyna + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(patchy ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(patchy ~ tDelayDyna + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Combined plots

### Response type (Fig.4)
```{r, fig.height=3, fig.width=9}
if(out){jpeg('mc_ct-rT_respType_fig4.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pStat + ggtitle('a') + theme(legend.position='none'),
             pDyna + ggtitle('b'), ncol=2, widths=c(2.21/5,2.79/5))
if(out){dev.off()}
```

### Individual data (SF.5)
```{r, fig.height=5, fig.width=9}
if(out){jpeg('mc_ct-rT_respType_sf5.jpg', width=7, height=4.2, units='in', res=600)}
grid.arrange(pStatIndiv + ggtitle('a') + theme(legend.position='none'),
             pDynaIndiv + ggtitle('b') + theme(legend.position='bottom'), 
             nrow=2, heights=c(2.22/5,2.78/5))
if(out){dev.off()}
```

# Center size

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
ss$y <- ss$ringSzP
sumSs <- sumFn(ss, xStr='tDelayStat')
sumSsAve <- sumSs[sumSs$subj=='average',]
pStatSz <- plotAve(pss=sumSsAve, xStr='tDelayStat', xlab=xLabStat, ylab=yLabSz)
pStatIndivSz <- plotIndiv(pss=sumSs, xStr='tDelayStat', xlab=xLabStat, ylab=yLabSz)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### center size ~ static delay
```{r}
ss <- ss[ss$resp=='static',]
summary(lmer(ringSzP ~ tDelayStat + (1|subj), data=ss))
summary(lm(ringSzP ~ tDelayStat, data=ss))
bfBase <- lmBF(ringSzP ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(ringSzP ~ tDelayStat + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
ss$y <- ss$ringSzP
sumSs <- sumFn(ss, xStr='tDelayDyna')
sumSsAve <- sumSs[sumSs$subj=='average',]
pDynaSz <- plotAve(pss=sumSsAve, xStr='tDelayDyna', xlab=xLabDyna, ylab=yLabSz)
pDynaIndivSz <- plotIndiv(pss=sumSs, xStr='tDelayDyna', xlab=xLabDyna, ylab=yLabSz)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### center size ~ dynamic delay
```{r}
ss <- ss[ss$resp=='static',]
summary(lmer(ringSzP ~ tDelayDyna + (1|subj), data=ss))
summary(lm(ringSzP ~ tDelayDyna, data=ss))
bfBase <- lmBF(ringSzP ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(ringSzP ~ tDelayDyna + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Combined plots

### Average data
```{r, fig.height=3, fig.width=9}
if(out){jpeg('mc_ct-rT_sz.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pStatSz + ggtitle('a') + theme(legend.position='none'),
             pDynaSz + ggtitle('b'), ncol=2, widths=c(2.21/5,2.79/5))
if(out){dev.off()}
```

### Individual data
```{r, fig.height=5, fig.width=9}
if(out){jpeg('mc_ct-rT_sz_indiv.jpg', width=7, height=4.2, units='in', res=600)}
grid.arrange(pStatIndivSz + ggtitle('a') + theme(legend.position='none'),
             pDynaIndivSz + ggtitle('b') + theme(legend.position='bottom'), 
             nrow=2, heights=c(2.22/5,2.78/5))
if(out){dev.off()}
```

# Center/surround

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
ss$y <- ss$ring
sumSs <- sumFn(ss, xStr='tDelayStat')
sumSsAve <- sumSs[sumSs$subj=='average',]
pStatCS <- plotAve(pss=sumSsAve, xStr='tDelayStat', xlab=xLabStat, ylab=yLabCS)
pStatIndivCS <- plotIndiv(pss=sumSs, xStr='tDelayStat', xlab=xLabStat, ylab=yLabCS)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### center/surround ~ static delay
```{r}
ss <- ss[ss$resp=='static',]
summary(glmer(ring ~ tDelayStat + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(ring ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(ring ~ tDelayStat + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
ss$y <- ss$ring
sumSs <- sumFn(ss, xStr='tDelayDyna')
sumSsAve <- sumSs[sumSs$subj=='average',]
pDynaCS <- plotAve(pss=sumSsAve, xStr='tDelayDyna', xlab=xLabDyna, ylab=yLabCS)
pDynaIndivCS <- plotIndiv(pss=sumSs, xStr='tDelayDyna', xlab=xLabDyna, ylab=yLabCS)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### center/surround ~ dynamic delay
```{r}
ss <- ss[ss$resp=='static',]
summary(glmer(ring ~ tDelayDyna + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(ring ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(ring ~ tDelayDyna + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## Combined plots

### Average data
```{r, fig.height=3, fig.width=9}
if(out){jpeg('mc_ct-rT_cs.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pStatCS + ggtitle('a') + theme(legend.position='none'),
             pDynaCS + ggtitle('b'), ncol=2, widths=c(2.21/5,2.79/5))
if(out){dev.off()}
```

### Individual data
```{r, fig.height=5, fig.width=9}
if(out){jpeg('mc_ct-rT_cs_indiv.jpg', width=7, height=4.2, units='in', res=600)}
grid.arrange(pStatIndivCS + ggtitle('a') + theme(legend.position='none'),
             pDynaIndivCS + ggtitle('b') + theme(legend.position='bottom'), 
             nrow=2, heights=c(2.22/5,2.78/5))
if(out){dev.off()}
```