---
title: "Motion clouds rivalry: Relative onset / Delay"
author: "Egor Ananyev"
date: "April 23, 2017"
output:
    html_document:
      toc: yes
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
library(lme4)
library(BayesFactor)
library(gridExtra)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
#db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcEcc_ct-tRelXbv'
subjs <- c(0:3)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
allDirs <- allDirs[grep(paste(expt,'_p',sep=''), allDirs)]
```

## Plot variables
```{r, message=FALSE, warning=FALSE}
# theme for plotting:
dodge <- position_dodge(width=0)
alpha <- .8
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=unit(-.04, 'in'),
            legend.background = element_rect(fill='transparent'),
            plot.title=element_text(face='bold'))
}
cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
```

## Summary function
```{r}
# computes individual and group means and SDs; req's y to be the var of interest
sumFn <- function(ss, subjStr, xStr, grpStr){
    sumSubj <- ddply(ss, c(subjStr, xStr, grpStr), summarise,
                     mnS=mean(y), se=sd(y)/sqrt(length(y)))
    sumGrp <- ddply(sumSubj, c(xStr, grpStr), summarise,
                  mn=mean(mnS), se=sd(mnS)/sqrt(length(mnS)))
    sumGrp$subj <- 'average'
    sumSubj <- rename(sumSubj, c(mnS='mn'))
    sumComb <- rbind(sumGrp, sumSubj)
    sumComb$se[is.na(sumComb$se)] <- 0
    sumComb
}
```

## Loading the data
```{r}
colsOfInt <- c('participant','session','trialN', #info
               'trialT', 'tOffL', 'tOffR', 'BvL', 'BvR', #IVs
               'nf000','nf090','nf180','nf270','ringSz') #DVs
df <- data.frame()
for(curSess in allDirs){
    print(curSess)
    sessFn <- paste(condDir, curSess, '/', curSess, '.csv', sep='')
    if(file.exists(sessFn)){
        curDs <- read.csv(sessFn)
        df <- rbind(df, curDs[,colsOfInt])
    }
}
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df #[colsOfInt]
ds <- rename(ds, c(participant='subj', session='sess', tOffL='tDelayL', 
                   tOffR='tDelayR'))
# Size conversions:
ds$ringSzDeg <- round((ds$ringSz+32)/35,1)
ds$ringSzP <- round(ds$ringSzDeg/max(ds$ringSzDeg),2)
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSzP < 1] <- 1
# tDelaySlow/fast
ds$tDelayStat <- 0
ds$tDelayStat[ds$BvL==0.01] <- ds$tDelayL[ds$BvL==0.01]
ds$tDelayStat[ds$BvR==0.01] <- ds$tDelayR[ds$BvR==0.01]
ds$tDelayDyna <- 0
ds$tDelayDyna[ds$BvL==9.6] <- ds$tDelayL[ds$BvL==9.6]
ds$tDelayDyna[ds$BvR==9.6] <- ds$tDelayR[ds$BvR==9.6]
head(ds)
```

# Types of responses
```{r}
# noDir, fastDir, slowDir, transparent
ds$slow <- 0
ds$slow[ds$nf270==1] <- 1
ds$fast <- 0
ds$fast[ds$nf180==1] <- 1
ds$patchy <- 0
ds$patchy[ds$nf090==1] <- 1
ds$transp <- 0
ds$transp[ds$nf000==1] <- 1
ds$resp[ds$slow==1] <- 'static'
ds$resp[ds$fast==1] <- 'dynamic'
ds$resp[ds$patchy==1] <- 'patchy'
ds$resp[ds$transp==1] <- 'transparent'
ds$resp <- factor(ds$resp, levels = c('static','dynamic','patchy','transparent'))
head(ds)
```

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
respStatSubj <- ddply(ss, .(subj, tDelayStat, resp), summarise, 
                      numSubjResp = length(subj))
respStat <- ddply(respStatSubj, .(tDelayStat, subj), summarise, 
                  totResp = sum(numSubjResp))
respStatSubj <- merge(respStatSubj, respStat, by=c('subj','tDelayStat'))
respStatSubj$pSubjResp <- with(respStatSubj, numSubjResp/totResp)
respStat <- ddply(respStatSubj, .(tDelayStat, resp), summarise,
                  pResp = mean(pSubjResp), seResp=sd(pSubjResp)/sqrt(length(subj)))
respStat$tDelayStat <- round(respStat$tDelayStat,1)
# respStat$tDelayStat <- as.factor(respStat$tDelayStat)
head(respStat)
```

```{r}
# merging two datasets:
respStat$subj <- 'average'
respStatSubj$pResp <- respStatSubj$pSubjResp
respStatSubj$seResp <- NA
respStatComb <- rbind(respStat,respStatSubj[,c('subj','tDelayStat','resp','pResp','seResp')])
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(respStat, aes(x=tDelayStat, y=pResp, colour=resp, group=resp,
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x='Static Stimulus Delay (s)',
         y='Proportion of Trials', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
pStat <- p + ggtitle('a') + theme(legend.position='none')
# if(!out){plot(p)}else{png('mc_ct-relT_respStat.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(respStatComb, aes(x=as.numeric(tDelayStat), y=pResp, colour=resp, group=resp, #)) +
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    facet_grid(. ~ factor(subj)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.2,.4,.6,.8,1), labels=c('0','','','','','1'), limits=c(0,1)) +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1), labels=c('0','','0.5','','1')) +
    labs(x='Static Stimulus Delay (s)',
         y='Proportion of Trials', colour='Response\nType') + #ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
pDynaIndiv <- p + ggtitle('a') + theme(legend.position='none')
# if(!out){plot(p)}else{png('mc_ct-relT_respStat_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
respDynaSubj <- ddply(ss, .(subj, tDelayDyna, resp), summarise, numSubjResp = length(subj))
respDyna <- ddply(respDynaSubj, .(tDelayDyna, subj), summarise, totResp = sum(numSubjResp))
respDynaSubj <- merge(respDynaSubj, respDyna, by=c('subj','tDelayDyna'))
respDynaSubj$pSubjResp <- with(respDynaSubj, numSubjResp/totResp)
respDyna <- ddply(respDynaSubj, .(tDelayDyna, resp), summarise,
                  pResp = mean(pSubjResp), seResp=sd(pSubjResp)/sqrt(length(subj)))
respDyna$tDelayDyna <- round(respDyna$tDelayDyna,1)
# respDyna$tDelayDyna <- as.factor(respDyna$tDelayDyna)
head(respDyna)
```

```{r}
# merging two datasets:
respDyna$subj <- 'average'
respDynaSubj$pResp <- respDynaSubj$pSubjResp
respDynaSubj$seResp <- NA
respDynaComb <- rbind(respDyna,respDynaSubj[,c('subj','tDelayDyna','resp','pResp','seResp')])
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(respDyna, aes(x=tDelayDyna, y=pResp, colour=resp, group=resp,
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x='Dynamic Stimulus Delay (s)',
         y='Proportion of Trials', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
pDyna <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-relT_respDyna.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(respDynaComb, aes(x=tDelayDyna, y=pResp, colour=resp, group=resp, #)) +
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    facet_grid(. ~ subj) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.2,.4,.6,.8,1), labels=c('0','','','','','1'), limits=c(0,1)) +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1), labels=c('0','','0.5','','1')) +
    labs(x='Dynamic Stimulus Delay (s)',
         y='Proportion of Trials', colour='Response Type') + #ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
pStatIndiv <- p + ggtitle('b') + theme(legend.position='bottom')
# if(!out){plot(p)}else{png('mc_ct-relT_respDyna_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
```


## Combined plots

### Response type (Fig.4)
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-rT_respType_fig4.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pStat, pDyna, ncol=2, widths=c(2.21/5,2.79/5))
if(out){dev.off()}
```

### Individual data (SF.5)
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-rT_respType_sf5.jpg', width=7, height=4.2, units='in', res=600)}
grid.arrange(pDynaIndiv, pStatIndiv, nrow=2, heights=c(2.22/5,2.78/5))
if(out){dev.off()}
```

# Center size

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
ss$y <- ss$ringSzP
sumSs <- sumFn(ss, 'subj', 'tDelayStat', 'resp')
```

```{r}
# merging two datasets:
sumRingSzP$subj <- 'average'
sumRingSzPSubj <- rename(sumRingSzPSubj, c(ringSzPSubj='ringSzP', ringSzPSubjSe='ringSzPSe'))
szStatComb <- rbind(sumRingSzP,sumRingSzPSubj[,c('subj','tDelayStat','resp','ringSzP','ringSzPSe')])
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingSzP, aes(x=tDelayStat, y=ringSzP, colour=resp, group=resp,
                        ymin=ringSzP-ringSzPSe, ymax=ringSzP+ringSzPSe)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x='Static Stimulus Delay (s)',
         y='Center/Stimulus Size',
         colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-tRel_ringSzStat.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(szStatComb, aes(x=tDelayStat, y=ringSzP, colour=resp, group=resp,
                        ymin=ringSzP-ringSzPSe, 
                        ymax=ringSzP+ringSzPSe)) +
    facet_grid(. ~ subj) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.5,1), labels=c('0','0.5','1'), limits=c(0,1)) + 
    labs(x='Static Stimulus Delay (s)',
         y='Center/Stimulus Size', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-relT_respSzStat_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
sumRingSzPSubj <- ddply(ss, .(subj, tDelayDyna, resp), summarise,
                       ringSzPSubj = mean(ringSzP),
                       ringSzPSubjSe = sd(ringSzP)/sqrt(length(ringSzP)))
sumRingSzP <- ddply(sumRingSzPSubj, .(resp, tDelayDyna), summarise,
                  ringSzP = mean(ringSzPSubj), 
                  ringSzPSe = sd(ringSzPSubj)/sqrt(length(subj)))
sumRingSzP$tDelayDyna <- round(sumRingSzP$tDelayDyna,1)
sumRingSzP$tDelayDyna <- as.factor(sumRingSzP$tDelayDyna)
sumRingSzPSubj$ringSzPSubjSe[is.na(sumRingSzPSubj$ringSzPSubjSe)] <- 0
head(sumRingSzP)
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingSzP, aes(x=tDelayDyna, y=ringSzP, colour=resp, group=resp,
                        ymin=ringSzP-ringSzPSe, ymax=ringSzP+ringSzPSe)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x='Dynamic Stimulus Delay (s)',
         y='Center/Stimulus Size',
         colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-tRel_ringSzDyna.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(sumRingSzPSubj, aes(x=tDelayDyna, y=ringSzPSubj, colour=resp, group=resp,
                        ymin=ringSzPSubj-ringSzPSubjSe, 
                        ymax=ringSzPSubj+ringSzPSubjSe)) +
    facet_grid(. ~ subj) + 
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.5,1), labels=c('0','0.5','1'), limits=c(0,1)) + 
    labs(x='Dynamic Stimulus Delay (s)',
         y='Center/Stimulus Size', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-relT_respSzDyna_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
```

# Proportion center/surround (inset)

## Static delay
```{r}
ss <- ds[ds$tDelayDyna==0,]
sumRingPSubj <- ddply(ss, .(subj, tDelayStat, resp), summarise,
                       ringPSubj = mean(ring),
                       ringPSubjSe = sd(ring)/sqrt(length(ring)))
sumRingP <- ddply(sumRingPSubj, .(resp, tDelayStat), summarise,
                  ringP = mean(ringPSubj), 
                  ringPSe = sd(ringPSubj)/sqrt(length(subj)))
sumRingP$tDelayStat <- as.factor(sumRingP$tDelayStat)
sumRingPSubj$ringPSubjSe[is.na(sumRingPSubj$ringPSubjSe)] <- 0
#head(sumRingP)
sumRingP
paste('mean proportion CS =', as.character(mean(sumRingP$ringP[sumRingP$resp=='static'])))
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingP, aes(x=tDelayStat, y=ringP, colour=resp, group=resp,
                        ymin=ringP-ringPSe, ymax=ringP+ringPSe)) +
    geom_point(position=dodge, size=.5, alpha=alpha, show.legend = F) +
    geom_line(position=dodge, alpha=alpha, show.legend = F) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank())
if(!out){plot(p)}else{png('mc_ct-tRel_ringPstat_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(sumRingPSubj, aes(x=tDelayStat, y=ringPSubj, colour=resp, group=resp,
                        ymin=ringPSubj-ringPSubjSe, 
                        ymax=ringPSubj+ringPSubjSe)) +
    facet_grid(. ~ subj) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.5,1), labels=c('0','0.5','1'), limits=c(0,1)) + 
    labs(x='Static Stimulus Delay (s)',
         y='Proportion Center-Surround', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-relT_respCSStat_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
# if(out){png('mc_ct-relT_respCSStat_indiv_lowres.png', width=7, height=2.1, units='in', res=150); plot(p); dev.off()}
```

## Dynamic delay
```{r}
ss <- ds[ds$tDelayStat==0,]
sumRingPSubj <- ddply(ss, .(subj, tDelayDyna, resp), summarise,
                       ringPSubj = mean(ring),
                       ringPSubjSe = sd(ring)/sqrt(length(ring)))
sumRingP <- ddply(sumRingPSubj, .(resp, tDelayDyna), summarise,
                  ringP = mean(ringPSubj), 
                  ringPSe = sd(ringPSubj)/sqrt(length(subj)))
sumRingP$tDelayDyna <- as.factor(sumRingP$tDelayDyna)
sumRingPSubj$ringPSubjSe[is.na(sumRingPSubj$ringPSubjSe)] <- 0
# head(sumRingP)
sumRingP
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingP, aes(x=tDelayDyna, y=ringP, colour=resp, group=resp,
                        ymin=ringP-ringPSe, ymax=ringP+ringPSe)) +
    geom_point(position=dodge, size=.5, alpha=alpha, show.legend = F) +
    geom_line(position=dodge, alpha=alpha, show.legend = F) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), 
                       panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank(), plot.background=element_rect(fill='grey'),
        axis.text.y = element_text(size=6))
if(!out){plot(p)}else{png('mc_ct-tRel_ringPdyna_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```

### Individual data
```{r, fig.height=2.1, fig.width=7}
p <- ggplot(sumRingPSubj, aes(x=tDelayDyna, y=ringPSubj, colour=resp, group=resp,
                        ymin=ringPSubj-ringPSubjSe, 
                        ymax=ringPSubj+ringPSubjSe)) +
    facet_grid(. ~ subj) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=c(0,.5,1), labels=c('0','0.5','1'), limits=c(0,1)) + 
    labs(x='Dynamic Stimulus Delay (s)',
         y='Proportion Center-Surround', colour='Response\nType') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-relT_respCSStat_indiv.png', width=7, height=2.1, units='in', res=600); plot(p); dev.off()}
```

# Analyses
```{r}
# Analysis
#library(lme4)
#library(lmerTest)
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
```