---
title: "Motion clouds rivalry: Translational velocity"
author: "Egor Ananyev"
date: "April 14, 2017"
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
library(lme4)
library(BayesFactor)
library(gridExtra)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
# db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcvct'
subjs <- c(0:3)
sesss <- c(1:3)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
```

## Plot variables
```{r}
# theme for plotting:
dodge <- position_dodge(width=0)
alpha <- .7
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=margin(t=-.04, unit='in'),
            legend.background = element_rect(fill='transparent'),
            plot.title=element_text(face='bold'))
}
#cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
cc <- c('#fed976','#c7e9b4','#7fcdbb','#41b6c4','#1d91c0','#225ea8','#0c2c84')
```

## Loading the data
```{r}
df <- data.frame()
for(curSubj in subjs){
    for(curSess in sesss){
        grepPattern <- paste(expt, '_p', curSubj, '_s', curSess, sep='')
        sessDir <- allDirs[grep(grepPattern, allDirs)]
        print(sessDir)
        sessFn <- paste(condDir, sessDir, '/', sessDir, '.csv', sep='')
        if(file.exists(sessFn)){
            curDs <- read.csv(sessFn)
            df <- rbind(df, curDs)
        }
    }
}
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df[c('participant','session','trialN','dirL','dirR','vL','vR','nf000','nf090',
           'nf180', 'nf270','ringSz')]
ds <- rename(ds, c(participant='subj', session='sess'))
ds$subj <- as.factor(ds$subj)
# Measuring velocities in dps:
ds$vR = round(ds$vR*60/35,1)
ds$vL = round(ds$vL*60/35,1)
ds$vR[ds$vR>=1] = round(ds$vR[ds$vR>=1])
ds$vL[ds$vL>=1] = round(ds$vL[ds$vL>=1])
head(ds)
```

## Adding new columns
```{r}
# Creating columns for the slower and faster of the two velocities:
ds$vMin <- rowMins(as.matrix(ds[c('vL','vR')]))
ds$vMax <- rowMaxs(as.matrix(ds[c('vL','vR')]))
ds$vDiff <- ds$vMax - ds$vMin
# The minimum size of the ring in the old paradigm corresponded to full field, so recoding:
ringSzMax=258
ds$ringSz[ds$ringSz==25.8] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==0,'ringSz']) & ds$subj==0] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==1,'ringSz']) & ds$subj==1] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==2,'ringSz']) & ds$subj==2] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==3,'ringSz']) & ds$subj==3] <- ringSzMax
ds$ringSzDeg <- ds$ringSz/35
ds$ringSzP <- ds$ringSz/258
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSz!=ringSzMax] <- 1
```


# Types of responses
```{r}
# noDir, fastDir, slowDir, transparent
ds$noDir <- 0
ds$noDir[ds$nf270==1] <- 1
ds$slowDir <- 0
ds$slowDir[ds$nf180==1 & ds$vL==ds$vMin & ds$vL!=ds$vR] <- 1
ds$slowDir[ds$nf000==1 & ds$vR==ds$vMin & ds$vL!=ds$vR] <- 1
ds$slow <- 0
ds$slow[ds$noDir==1] <- 1
ds$slow[ds$slowDir==1] <- 1
ds$fastDir <- 0
ds$fastDir[ds$nf180==1 & ds$vL==ds$vMax & ds$vL!=ds$vR] <- 1
ds$fastDir[ds$nf000==1 & ds$vR==ds$vMax & ds$vL!=ds$vR] <- 1
ds$transp <- 0
ds$transp[ds$nf090==1] <- 1
ds$resp <- ''
ds$resp[ds$vL==ds$vR] <- 'either\ndirection'
ds$resp[ds$noDir==1] <- 'no direction'
ds$resp[ds$slowDir==1] <- 'slow\ndirection'
ds$resp[ds$fastDir==1] <- 'fast\ndirection'
ds$resp[ds$transp==1] <- 'transparent/\npatchy'
ds$resp <- factor(ds$resp, levels = c('slow\ndirection','fast\ndirection','no direction',
                                      'transparent/\npatchy','either\ndirection'))
```

## Frequency table of response space
```{r}
sumRespSubj <- ddply(ds, .(subj, resp, ring), summarise, numSubjResp = length(subj))
sumResp <- ddply(sumRespSubj, .(subj), summarise, totSubjResp = sum(numSubjResp))
sumRespSubj <- merge(sumRespSubj, sumResp, by='subj')
sumRespSubj$pSubjResp <- with(sumRespSubj, numSubjResp/totSubjResp)
sumRespSE <- ddply(sumRespSubj, .(resp, ring), summarise,
                 seResp=sd(pSubjResp)/sqrt(length(subj)))
sumResp <- ddply(ds, .(resp, ring), summarise, numResp = length(subj))
sumResp$pResp <- sumResp$numResp / sum(sumResp$numResp)
sumResp <- merge(sumResp, sumRespSE, by=c('resp','ring'))
# write.table(sumResp,'clipboard',sep='\t',row.names=F, mode='r') #Windows
# write.table(sumResp,pipe('pbcopy'),sep='\t',row.names=F,col.names=F) #Mac
sumResp
```

## Slow
```{r}
sumSlowSubj <- ddply(ds, .(subj, vMin, vMax), summarise, 
                     pSubjResp = mean(slow))
sumSlow <- ddply(sumSlowSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

### Plots

#### 2D
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlow, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         color='Slow\nDominance\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
( p <- themefy(p) )
p2dSlow <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_slow2d2.png', width=3.2, height=2.1, units='in', res=600); plot(p); dev.off()}
```

##### vMin (inset)
```{r, fig.height=3, fig.width=5}
pSlowIn <- ggplot(sumSlow[sumSlow$vMin==0,], aes(x=factor(vMax), y=pResp, 
                                                 group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=.5, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,.5,1), labels=c('0','','1'), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), 
                       panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank(), plot.background=element_rect(fill='grey'),
        axis.text.y = element_text(size=6))
```

#### Slower velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlow, aes(x=factor(vMin), y=pResp, colour=factor(vMax), group=factor(vMax),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Slow Dominance', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pVmin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_slowVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Faster velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlow, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Slow Dominance', colour='\nLower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pVmax <- p + ggtitle('b') + theme(axis.title.y=element_blank())
# if(!out){plot(p)}else{png('mc_ct-v_slowVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_slow.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pVmin, pVmax, ncol=2, widths=c(2.6/5,2.4/5))
if(out){dev.off()}
```

### BF analyses
```{r}
summary(glmer(slow ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(slow ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(slow ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(slow ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(slow ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

## No-direction responses
```{r}
sumNoDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(noDir))
sumNoDir <- ddply(sumNoDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

### Plots

#### 2D
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumNoDir, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         color='No-Direction\nResponses\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
( p <- themefy(p) )
#p2dNoDir <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_noDir2d2.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Slower velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumNoDir, aes(x=factor(vMin), y=pResp, colour=factor(vMax), 
                          group=factor(vMax), ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='No-Direction Responses', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pVminNoDir <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_noDirVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Faster velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumNoDir, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='No-Direction Responses', colour='\nLower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pVmaxNoDir <- p + ggtitle('b') + theme(axis.title.y=element_blank())
# if(!out){plot(p)}else{png('mc_ct-v_noDirVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_noDir.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pVminNoDir, pVmaxNoDir, ncol=2, widths=c(2.6/5,2.4/5))
if(out){dev.off()}
```

### BF analyses
```{r}
summary(glmer(noDir ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(noDir ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(noDir ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(noDir ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(noDir ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

<!--
```{r}
# sumNoDirSubjDiff <- ddply(ds, .(subj, vDiff), summarise, pSubjResp = mean(noDir))
# sumNoDirDiff <- ddply(sumNoDirSubjDiff, .(vDiff), summarise,
#                   pResp = mean(pSubjResp), 
#                   seResp = sd(pSubjResp)/sqrt(length(subj)))
```

## vDiff
```{r, fig.height=3, fig.width=5}
# p <- ggplot(sumNoDirDiff, aes(x=vDiff, y=pResp, ymin=pResp-seResp, ymax=pResp+seResp)) +
#     geom_point(position=dodge, size=1, alpha=alpha) +
#     geom_line(position=dodge, alpha=alpha) +
#     geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
#     labs(x=expression(paste('Velocity Difference (', degree, '/s)', sep='')), 
#          y='No-Direction Responses (p)') + ylim(0,1) +
#     guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
# p <- themefy(p)
# if(!out){plot(p)}else{png('mc_ct-v_noDirVdiff.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```
--->

## Slow/Fast direction

### Slow-direction
```{r}
sumSlowDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(slowDir))
sumSlowDir <- ddply(sumSlowDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlowDir, aes(x=factor(vMin), y=pResp, colour=factor(vMax), 
                            group=factor(vMax), ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Slow-Direction Responses', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pSlowDir <- p + ggtitle('a') + theme(legend.position='none')
# if(!out){plot(p)}else{png('mc_ct-v_slowDirVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

<!--
### Inset
```{r, echo=FALSE}
p <- ggplot(sumSlowDir[sumSlowDir$vMin==0,], aes(x=factor(vMax), y=pResp, 
                         group=factor(vMin), ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=1) +
    geom_line(position=dodge, alpha=1) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), 
        panel.grid.minor.y=element_blank(), axis.text.x = element_blank(), 
        axis.title=element_blank(), axis.text=element_text(size=6),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank())
if(out){png('mc_ct-v_slowDir_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlowDir, aes(x=factor(vMax), y=pResp, colour=factor(vMin), 
                            group=factor(vMin), ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Slow-Direction Responses', colour='Lower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
# if(!out){plot(p)}else{png('mc_ct-v_slowDirVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```
--->

```{r}
summary(glmer(slowDir ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(slowDir ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(slowDir ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(slowDir ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(slowDir ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

### Fast-direction
```{r}
sumFastDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(fastDir))
sumFastDir <- ddply(sumFastDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumFastDir, aes(x=factor(vMin), y=pResp, colour=factor(vMax), 
                            group=factor(vMax), ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Fast-Direction Responses', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pFastDir <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_fastDirVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

<!--
```{r, echo=FALSE}
p <- ggplot(sumFastDir[sumFastDir$vMin==0,], aes(x=factor(vMax), y=pResp, group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=1) +
    geom_line(position=dodge, alpha=1) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(), axis.text=element_text(size=6),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank())
if(out){png('mc_ct-v_fastDir_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumFastDir, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Fast-Direction Responses', colour='Lower Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_fastDirVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```
--->

```{r}
summary(glmer(fastDir ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(fastDir ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(fastDir ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(fastDir ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(fastDir ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

### Combined figure
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_slowFast.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pSlowDir, pFastDir, ncol=2, widths=c(2.35/5,2.65/5))
if(out){dev.off()}
```

## Directional
```{r}
sumDirSubj <- ddply(ds[ds$slowDir+ds$fastDir==1,], 
                        .(subj, vMin, vMax), summarise, pSubjResp = mean(slowDir))
sumDir <- ddply(sumDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

### Plots

#### 2D
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumDir, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         color='Directional\nResponses\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
( p <- themefy(p) )
#p2dNoDir <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_dir2d2.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Slower velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumDir, aes(x=factor(vMin), y=pResp, colour=factor(vMax), group=factor(vMax),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Directional Responses', colour='Higher\nVelocity') + #ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pDirMin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_dirVmin.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

#### Higher velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumDir, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Directional Responses', colour='\nLower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pDirMax <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_dirVmax.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_dir.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pDirMin, pDirMax, ncol=2, widths=c(2.5/5,2.5/5))
if(out){dev.off()}
```

### BF analyses
```{r}
ds$anyDir <- ds$slowDir + ds$fastDir
summary(glmer(anyDir ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(anyDir ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(anyDir ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(anyDir ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(anyDir ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

### T-test
```{r}
sumDirDiff <- merge(sumSlowDir, sumFastDir, by=c('vMin','vMax'))
t.test(sumDirDiff$pResp.x,sumDirDiff$pResp.y,paired=T)
```

## Transparency
```{r}
sumTranspSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(transp))
sumTransp <- ddply(sumTranspSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumTransp, aes(x=factor(vMin), y=pResp, colour=factor(vMax), group=factor(vMax),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Transparency Responses', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pTranspMin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_transpVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

<!--
```{r, echo=FALSE}
p <- ggplot(sumTransp[sumTransp$vMin==0,], aes(x=factor(vMax), y=pResp, group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=1) +
    geom_line(position=dodge, alpha=1) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(), axis.text=element_text(size=6),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank())
if(out){png('mc_ct-v_transp_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```
--->

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumTransp, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Transparency Responses', colour='Lower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pTranspMax <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_transpVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
# if(out){jpeg('mc_ct-v_dir.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pTranspMin, pTranspMax, ncol=2, widths=c(2.5/5,2.5/5))
# if(out){dev.off()}
```

```{r}
summary(glmer(transp ~ vMin * vMax + (1|subj), data=ds, family='binomial'))
bfVmin <- lmBF(transp ~ vMin + subj, data=ds, whichRandom = 'subj')
bfVmax <- lmBF(transp ~ vMax + subj, data=ds, whichRandom = 'subj')
bfSum <- lmBF(transp ~ vMin + vMax + subj, data=ds, whichRandom = 'subj')
bfInt <- lmBF(transp ~ vMin * vMax + subj, data=ds, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

# Center-surround

## Center-surround / whole-field frequencies
```{r}
ds$scfs <- 0 # slow center / fast surround
ds$scfs[ds$ring==1 & (ds$resp=='no direction' | ds$resp=='slow\ndirection')] <- 1
ds$fcss <- 0
ds$fcss[ds$ring==1 & ds$resp=='fast\ndirection'] <- 1
ds$sw <- 0 # slow whole field
ds$sw[ds$ring==0 & (ds$resp=='no direction' | ds$resp=='slow\ndirection')] <- 1
ds$fw <- 0
ds$fw[ds$ring==0 & ds$resp=='fast\ndirection'] <- 1
sumCsSubj <- ddply(ds, .(subj, vMin, vMax), summarise,
                       pSubjScfs = mean(scfs), pSubjFcss = mean(fcss),
                       pSubjSw = mean(sw), pSubjFw = mean(fw))
sumCs <- ddply(sumCsSubj, .(vMin, vMax), summarise,
                  pScfs = mean(pSubjScfs), seScfs = sd(pSubjScfs)/sqrt(length(subj)),
                  pFcss = mean(pSubjFcss), seFcss = sd(pSubjFcss/sqrt(length(subj))),
                  pSw = mean(pSubjSw), seSw = sd(pSubjSw)/sqrt(length(subj)),
                  pFw = mean(pSubjFw), seFw = sd(pSubjFw/sqrt(length(subj))))
# sumRing$pResp[which(is.na(sumRing$seResp))] <- NA
#sumRing <- sumRing[!is.na(sumRing$seResp),]
head(sumCs)
```

## Slow-center/fast-surround

### Slower along x
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumCs, aes(x=factor(vMin), y=pScfs, colour=factor(vMax), group=factor(vMax),
                        ymin=pScfs-seScfs, ymax=pScfs+seScfs)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Slow-Center/Fast-Surround', colour='Higher Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pSCFSmin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_scfsVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Faster along x
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumCs, aes(x=factor(vMax), y=pScfs, colour=factor(vMin), group=factor(vMin),
                        ymin=pScfs-seScfs, ymax=pScfs+seScfs)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Slow-Center/Fast-Surround', colour='Lower Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pSCFS <- p + ggtitle('a')
pSCFSmax <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_scfsVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
# if(out){jpeg('mc_ct-v_dir.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pSCFSmin, pSCFSmax, ncol=2, widths=c(2.5/5,2.5/5))
# if(out){dev.off()}
```

## Fast-center/slow-surround

### Slower along x
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumCs, aes(x=factor(vMin), y=pFcss, colour=factor(vMax), group=factor(vMax),
                        ymin=pFcss-seFcss, ymax=pFcss+seFcss)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Fast-Center/Slow-Surround', colour='Higher Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pFCSSmin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_fcssVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Faster along x
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumCs, aes(x=factor(vMax), y=pFcss, colour=factor(vMin), group=factor(vMin),
                        ymin=pFcss-seFcss, ymax=pFcss+seFcss)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Fast-Center/Slow-Surround', colour='Lower Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pFCSSmax <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_fcssVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Combined figure
```{r, fig.height=2.1, fig.width=7}
#if(out){jpeg('mc_ct-v_dir.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pFCSSmin, pFCSSmax, ncol=2, widths=c(2.5/5,2.5/5))
#if(out){dev.off()}
```

# Slow-center/fast-surround among slow
```{r}
sumRingSubj <- ddply(ds[ds$slow==1,], .(subj, vMin, vMax), summarise,
                       nSubjResp = sum(ring), pSubjResp = mean(ring))
sumRing <- ddply(sumRingSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), nResp = mean(nSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumRing$pResp[which(is.na(sumRing$seResp))] <- NA
sumRing <- sumRing[!is.na(sumRing$seResp),]
```

## Plots

### 2D

#### Number
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMin), y=factor(vMax), color=nResp)) + 
    geom_point(size=4) + 
    scale_colour_gradient(limits=c(0,9), breaks=c(0,3,6,9)) + #, breaks=c(0,.5,1)) +
    geom_point(data=sumRing, shape=1, aes(x=factor(vMin), y=factor(vMax), size=9),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Center-\nSurround\n(N trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4)) + ggtitle('b')
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_ringV2d2n.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### Proportion
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumRing, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         color='Center/\nSurround\n(P Trials)\n') +
    guides(color=guide_colorbar(barwidth=1, barheight=4))
p <- themefy(p)
pCS <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_ringV2d2p.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

#### vMin (inset)
```{r, fig.height=3, fig.width=5}
pCSIn <- ggplot(sumRing[sumRing$vMin==0,], aes(x=factor(vMax), y=pResp, 
                                                 group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=.5, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,.5,1), labels=c('0','','1'), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), 
                       panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank(), plot.background=element_rect(fill='grey'),
        axis.text.y = element_text(size=6))
```

### Slower velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMin), y=pResp, colour=factor(vMax), group=factor(vMax),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Slow-Center/Fast-Surround', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[2:7])
p <- themefy(p)
pCSmin <- p + ggtitle('a')
# if(!out){plot(p)}else{png('mc_ct-v_ringVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Faster velocity along x-axis
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMax), y=pResp, colour=factor(vMin), group=factor(vMin),
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Slow-Center/Fast-Surround', colour='Lower\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
pCSmax <- p + ggtitle('b')
# if(!out){plot(p)}else{png('mc_ct-v_ringVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### Combined figure
```{r, fig.height=2.1, fig.width=7}
# if(out){jpeg('mc_ct-v_cs.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pCSmin, pCSmax, ncol=2, widths=c(2.5/5,2.5/5))
# if(out){dev.off()}
```

## BF analysis
```{r}
ss <- ds[ds$resp=='no direction',]
ss <- ss[!is.na(ss$ring),]
summary(glmer(ring ~ vMin * vMax + (1|subj), data=ss, family='binomial'))
bfVmin <- lmBF(ring ~ vMin + subj, data=ss, whichRandom = 'subj')
bfVmax <- lmBF(ring ~ vMax + subj, data=ss, whichRandom = 'subj')
bfSum <- lmBF(ring ~ vMin + vMax + subj, data=ss, whichRandom = 'subj')
bfInt <- lmBF(ring ~ vMin * vMax + subj, data=ss, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

## Center size: Proportion of ring size
```{r}
sumRingSzPSubj <- ddply(ds[ds$resp=='no direction' & ds$ring==1,], .(subj, vMin, vMax), summarise,
                       ringSzPSubj = mean(ringSzP), ringN = sum(ring))
sumRingSzP <- ddply(sumRingSzPSubj[sumRingSzPSubj$ringN>1,], .(vMin, vMax), summarise,
                  ringSzP = mean(ringSzPSubj), 
                  ringN = mean(ringN), 
                  ringSzPSe = sd(ringSzPSubj)/sqrt(length(subj)))
# sumRingSzP$ringSzP[which(is.na(sumRingSzP$ringSzPSe))] <- NA
sumRingSzP <- sumRingSzP[!is.na(sumRingSzP$ringSzPSe),]
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingSzP[sumRingSzP$vMax>=8,], aes(x=factor(vMin), y=ringSzP, colour=factor(vMax), group=factor(vMax),
                        ymin=ringSzP-ringSzPSe, ymax=ringSzP+ringSzPSe)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Lower Velocity (', degree, '/s)', sep='')), 
         y='Center Size', colour='Higher\nVelocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc[c(5,7)])
p <- themefy(p)
pRingSzMin <- p + ggtitle('b')
if(!out){plot(p)}else{png('mc_ct-v_ringSzPVmin.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

<!--
```{r, echo=FALSE}
p <- ggplot(sumRingSzP[sumRingSzP$vMax>16,], aes(x=factor(vMin), y=ringSzP, 
                 group=factor(vMax), ymin=ringSzP-ringSzPSe, ymax=ringSzP+ringSzPSe)) +
    geom_line(position=dodge, alpha=1) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,1), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
        axis.text.x = element_text(size=4), axis.title=element_blank(), 
        axis.text=element_text(size=4),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank())
if(out){png('mc_ct-v_ringSzP_inset.png', width=.8, height=.6, units='in', res=600); plot(p); dev.off()}
```
--->

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRingSzP, aes(x=factor(vMax), y=ringSzP, colour=factor(vMin), group=factor(vMin),
                        ymin=ringSzP-ringSzPSe, ymax=ringSzP+ringSzPSe)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    labs(x=expression(paste('Higher Velocity (', degree, '/s)', sep='')), 
         y='Center Size', colour='Lower Velocity') + ylim(0,1) +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_colour_manual(values=cc)
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_ringSzPVmax.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

```{r}
ss <- ds[ds$resp=='no direction' & ds$ring==1,]
ss <- ss[!is.na(ss$ring),]
summary(glmer(ringSzP ~ vMin * vMax + (1|subj), data=ss, family='binomial'))
bfVmin <- lmBF(ringSzP ~ vMin + subj, data=ss, whichRandom = 'subj')
bfVmax <- lmBF(ringSzP ~ vMax + subj, data=ss, whichRandom = 'subj')
bfSum <- lmBF(ringSzP ~ vMin + vMax + subj, data=ss, whichRandom = 'subj')
bfInt <- lmBF(ringSzP ~ vMin * vMax + subj, data=ss, whichRandom = 'subj')
print(paste('vMax:', as.vector(bfSum / bfVmin)))
print(paste('vMin:', as.vector(bfSum / bfVmax)))
print(paste('interaction:', as.vector(bfInt / bfSum)))
```

# Additional combined figures

## FigS2
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_s2.jpg', width=7, height=2.1, units='in', res=600)}
grid.arrange(pCSmax + ggtitle('a'), pRingSzMin, ncol=2, widths=c(2.5/5,2.5/5))
if(out){dev.off()}
```

## Fig2: Slow & Center-Surround Trials
```{r, fig.height=2.1, fig.width=7}
if(out){jpeg('mc_ct-v_fig2.jpg', width=7, height=2.1, units='in', res=600)}
vp <- grid::viewport(x=.3135, y=.373, width=.12, height=.3)
vp2 <- grid::viewport(x=.835, y=.373, width=.11, height=.3)
grid.arrange(p2dSlow, pCS, ncol=2, widths=c(2.5/5,2.5/5))
print(pSlowIn, vp=vp)
print(pCSIn, vp=vp2)
if(out){dev.off()}
```
