---
title: "Motion clouds rivalry: Stimulus Size"
author: "Egor Ananyev"
date: "April 21, 2017"
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
library(lme4)
library(BayesFactor)
library(gridExtra)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
#db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcEcc_ct-szXbv'
subjs <- c(0:3)
sesss <- c(1:2)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
```

## Plot variables
```{r}
dodge <- position_dodge(width=0)
alpha <- .8
cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
xLab <- expression(paste('Stimulus Size (', degree, ')', sep=''))
xVar <- 'stimSzDeg'
yLab <- 'Proportion of Trials'
yLabSz <- 'Center/Stimulus Size'
yLabCS <- 'Proportion Center-Surround'
colLab <- 'Response\nType'
colLab2 <- 'Response Type' # for use in indiv plots where col label is along the bottom
```

## Plot functions
```{r, message=FALSE, warning=FALSE}
# theme for plotting:
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=margin(t=-.04, unit='in'),
            legend.background = element_rect(fill='transparent'),
            plot.title=element_text(face='bold'))
}
plotAve <- function(pss, subjStr='subj', xStr=xVar, grpStr='resp', 
                    xlab, ylab=yLab, collab=colLab, yStr='mn', seStr='se'){
    pss$yMin <- pss[,yStr] - pss[,seStr]
    pss$yMax <- pss[,yStr] + pss[,seStr]
    p <- ggplot(pss, aes_string(x=xStr, y=yStr, colour=grpStr, group=grpStr,
                            ymin='yMin', ymax='yMax')) +
        geom_point(position=dodge, size=1, alpha=alpha) + geom_line(position=dodge, alpha=alpha) +
        scale_x_continuous(breaks=c(3,3.7,4.3,5,5.7,6.4))+
        geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
        labs(x=xlab, y=ylab, colour=collab) +  ylim(0,1) + 
        guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
    p <- themefy(p)
}
plotIndiv <- function(pss, subjStr='subj', xStr=xVar, grpStr='resp', 
                    xlab, ylab=yLab, collab=colLab2, yStr='mn', seStr='se'){
    pss$yMin <- pss[,yStr] - pss[,seStr]
    pss$yMax <- pss[,yStr] + pss[,seStr]
    p <- ggplot(pss, aes_string(x=xStr, y=yStr, colour=grpStr, group=grpStr,
                            ymin='yMin', ymax='yMax')) + 
        facet_grid(paste('.~factor(', subjStr, ')', sep='')) +
        geom_point(position=dodge, size=1, alpha=alpha) + geom_line(position=dodge, alpha=alpha) +
        geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
        scale_x_continuous(breaks=c(3,3.7,4.3,5,5.7,6.4), labels=c('3','','','','','6.4'), limits=c(3,6.4))+
        scale_y_continuous(breaks=c(0,.25,.5,.75,1), labels=c('0','','0.5','','1'), limits=c(0,1)) +
        labs(x=xlab, y=ylab, colour=collab) + 
        guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
    p <- themefy(p)
}
```

## Summary functions
```{r}
# computes individual and group means and SDs; req's y to be the var of interest
sumFn <- function(ss, subjStr='subj', xStr=xVar, grpStr='resp'){
    sumSubj <- ddply(ss, c(subjStr, xStr, grpStr), summarise,
                     mnS=mean(y), se=sd(y)/sqrt(length(y))) #, .drop=F)
    # sumSubj$mnS[is.na(sumSubj$mnS)] <- 0
    sumGrp <- ddply(sumSubj, c(xStr, grpStr), summarise,
                  mn=mean(mnS), se=sd(mnS)/sqrt(length(mnS)))
    sumGrp$subj <- 'average'
    sumSubj <- rename(sumSubj, c(mnS='mn'))
    sumComb <- rbind(sumGrp, sumSubj)
    sumComb$se[is.na(sumComb$se)] <- 0
    sumComb
}
# computes the proportion of different levels of 'grpStr' -- here, response types
sumPFn <- function(ss, subjStr='subj', xStr=xVar, grpStr='resp'){
    sumSubj <- ddply(ss, c(subjStr, xStr, grpStr), summarise, nm = length(subj), .drop=F)
    sumGrp <- ddply(sumSubj, c(subjStr, xStr), summarise, tot=sum(nm))
    sumSubj <- merge(sumSubj, sumGrp, by=c(subjStr,xStr))
    sumSubj$pSubj <- with(sumSubj, nm/tot)
    sumGrp <- ddply(sumSubj, c(xStr, grpStr), summarise,
                  mn=mean(pSubj), se=sd(pSubj)/sqrt(length(subj)))
    sumSubj <- rename(sumSubj, c(pSubj='mn'))
    sumSubj$se <- 0
    sumGrp$subj <- 'average'
    sumComb <- rbind(sumGrp, sumSubj[,c(subjStr,xStr,grpStr,'mn','se')])
    sumComb$se[is.na(sumComb$se)] <- 0
    sumComb
}
```

## Loading the data
```{r}
colsOfInt <- c('participant','session','trialN', #info
               'periGap', #IVs
               'nf000','nf090','nf180','nf270','ringSz') #DVs
df <- data.frame()
for(curSubj in subjs){
    for(curSess in sesss){
        grepPattern <- paste(expt, '_p', curSubj, '_s', curSess, sep='')
        sessDir <- allDirs[grep(grepPattern, allDirs)]
        print(sessDir)
        sessFn <- paste(condDir, sessDir, '/', sessDir, '.csv', sep='')
        if(file.exists(sessFn)){
            curDs <- read.csv(sessFn)
            df <- rbind(df, curDs[,colsOfInt])
        }
    }
}
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df #[colsOfInt]
ds <- rename(ds, c(participant='subj', session='sess'))
ds$subj <- as.factor(ds$subj)
# Size conversions:
ds$stimSzDeg <- round((ds$periGap*2+32)/35,1)
ds$ringSzDeg <- round((ds$ringSz+32)/35,1)
ds$ringSzP <- round(ds$ringSzDeg/ds$stimSzDeg,2)
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSzDeg<ds$stimSzDeg] <- 1
head(ds)
```

# Types of responses
```{r}
# noDir, dynaDir, statDir, transparent
ds$stat <- 0
ds$stat[ds$nf270==1] <- 1
ds$dyna <- 0
ds$dyna[ds$nf180==1] <- 1
ds$patchy <- 0
ds$patchy[ds$nf090==1] <- 1
ds$transp <- 0
ds$transp[ds$nf000==1] <- 1
ds$resp[ds$stat==1] <- 'static'
ds$resp[ds$dyna==1] <- 'dynamic'
ds$resp[ds$patchy==1] <- 'patchy'
ds$resp[ds$transp==1] <- 'transp'
ds$resp <- factor(ds$resp, levels = c('static','dynamic','patchy','transparent'))
head(ds)
```

```{r}
sumSs <- sumPFn(ds)
sumSsAve <- sumSs[sumSs$subj=='average',]
pResp <- plotAve(pss=sumSsAve, xlab=xLab)
pRespIndiv <- plotIndiv(pss=sumSs[sumSs$subj!='average',], xlab=xLab)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

## stat dom ~ stim size
```{r}
summary(glmer(stat ~ stimSzDeg + (1|subj), data=ds, family='binomial'))
bfBase <- lmBF(stat ~ subj, data=ds, whichRandom = 'subj')
bfSz <- lmBF(stat ~ stimSzDeg + subj, data=ds, whichRandom='subj')
as.vector(bfSz / bfBase)
```

## patchy dom ~ stim size
```{r}
summary(glmer(patchy ~ stimSzDeg + (1|subj), data=ds, family='binomial'))
bfBase <- lmBF(patchy ~ subj, data=ds, whichRandom = 'subj')
bfSz <- lmBF(patchy ~ stimSzDeg + subj, data=ds, whichRandom='subj')
as.vector(bfSz / bfBase)
```

# Center size

## Center size (p)
```{r}
ss <- ds
ss$y <- ss$ringSzP
sumSs <- sumFn(ss)
sumSsAve <- sumSs[sumSs$subj=='average',]
pSz <- plotAve(pss=sumSsAve, xlab=xLab, ylab=yLabSz)
pIndivSz <- plotIndiv(pss=sumSs[sumSs$subj!='average',], xlab=xLab, ylab=yLabSz)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

### BF analyses
```{r}
summary(lmer(ringSzP ~ stimSzDeg + (1|subj), data=ds))
summary(lm(ringSzP ~ stimSzDeg, data=ds))
bfBase <- lmBF(ringSzP ~ subj, data=ds, whichRandom = 'subj')
bfSz <- lmBF(ringSzP ~ stimSzDeg + subj, data=ds, whichRandom='subj')
as.vector(bfSz / bfBase)
```

# Proportion center/surround
```{r}
ss <- ds
ss$y <- ss$ring
sumSs <- sumFn(ss)
sumSsAve <- sumSs[sumSs$subj=='average',]
pCs <- plotAve(pss=sumSsAve, xlab=xLab, ylab=yLabCS)
pIndivCs <- plotIndiv(pss=sumSs[sumSs$subj!='average',], xlab=xLab, ylab=yLabCS)
ddply(sumSsAve, .(resp), summarize, respMean=round(mean(mn),2), respSD=round(sd(mn),2))
```

## BF analyses
```{r}
ss <- ds[ds$stat==1,]
summary(glmer(ring ~ stimSzDeg + (1|subj), data=ss, family='binomial'))
bfBase <- lmBF(ring ~ subj, data=ss, whichRandom = 'subj')
bfSz <- lmBF(ring ~ stimSzDeg + subj, data=ss, whichRandom='subj')
as.vector(bfSz / bfBase)
```

# Combined plot
```{r, fig.height=4.2, fig.width=7}
if(out){jpeg('mc_ct-sz.jpg', width=7, height=3.8, units='in', res=600)}
grid.arrange(pResp + theme(legend.position='none') + ggtitle('a'), 
             pCs + theme(legend.position='none') + ggtitle('b'), 
             pSz + theme(legend.position='none') + ggtitle('c'), 
             pRespIndiv + ggtitle('d'), layout_matrix=rbind(c(1,2,3),c(4,4,4)))
if(out){dev.off()}
```