---
title: "Motion clouds rivalry: Translational velocity"
author: "Egor Ananyev"
date: "April 14, 2017"
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
#db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcvct'
subjs <- c(0:3)
sesss <- c(1:3)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
```

## Plot variables
```{r}
# theme for plotting:
dodge <- position_dodge(width=0)
alpha <- 1 #.6
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=unit(-.04, 'in'),
            legend.background = element_rect(fill='transparent'),
            plot.title=element_text(face='bold'))
}
cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
```

## Loading the data
```{r}
df <- data.frame()
for(curSubj in subjs){
    for(curSess in sesss){
        grepPattern <- paste(expt, '_p', curSubj, '_s', curSess, sep='')
        sessDir <- allDirs[grep(grepPattern, allDirs)]
        print(sessDir)
        sessFn <- paste(condDir, sessDir, '/', sessDir, '.csv', sep='')
        if(file.exists(sessFn)){
            curDs <- read.csv(sessFn)
            df <- rbind(df, curDs)
        }
    }
}
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df[c('participant','session','trialN','dirL','dirR','vL','vR','nf000','nf090','nf180',
           'nf270','ringSz')]
ds <- rename(ds, c(participant='subj', session='sess'))
# Measuring velocities in dps:
ds$vR = round(ds$vR*60/35,1)
ds$vL = round(ds$vL*60/35,1)
ds$vR[ds$vR>=1] = round(ds$vR[ds$vR>=1])
ds$vL[ds$vL>=1] = round(ds$vL[ds$vL>=1])
head(ds)
```

## Adding new columns
```{r}
# Creating columns for the slower and faster of the two speeds:
ds$vMin <- rowMins(as.matrix(ds[c('vL','vR')]))
ds$vMax <- rowMaxs(as.matrix(ds[c('vL','vR')]))
ds$vDiff <- ds$vMax - ds$vMin
```


# Types of responses
```{r}
# noDir, fastDir, slowDir, transparent
ds$noDir <- 0
ds$noDir[ds$nf270==1] <- 1
ds$slowDir <- 0
ds$slowDir[ds$nf180==1 & ds$vL==ds$vMin] <- 1
ds$slowDir[ds$nf000==1 & ds$vR==ds$vMin] <- 1
ds$fastDir <- 0
ds$fastDir[ds$nf180==1 & ds$vL==ds$vMax] <- 1
ds$fastDir[ds$nf000==1 & ds$vR==ds$vMax] <- 1
ds$transp <- 0
ds$transp[ds$nf090==1] <- 1
ds$slow <- 0
ds$slow[ds$noDir==1] <- 1
ds$slow[ds$slowDir==1] <- 1
ds$resp[ds$noDir==1] <- 'no direction'
ds$resp[ds$slowDir==1] <- 'slow\ndirection'
ds$resp[ds$fastDir==1] <- 'fast\ndirection'
ds$resp[ds$transp==1] <- 'transparent/\npatchy'
ds$resp <- factor(ds$resp, levels = c('slow\ndirection','fast\ndirection','no direction',
                                      'transparent/\npatchy')) 
# The minimum size of the ring in the old paradigm corresponded to full field, so recoding:
ringSzMax=258
ds$ringSz[ds$ringSz==25.8] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==0,'ringSz']) & ds$subj==0] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==1,'ringSz']) & ds$subj==1] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==2,'ringSz']) & ds$subj==2] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==3,'ringSz']) & ds$subj==3] <- ringSzMax
ds$ringSzDeg <- round(ds$ringSz/35,1)
ds$ringSzP <- round(ds$ringSz/258)
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSz!=ringSzMax] = 1
```

## Frequency table of response space
```{r}
sumRespSubj <- ddply(ds, .(subj, resp, ring), summarise, numSubjResp = length(subj))
sumResp <- ddply(sumRespSubj, .(subj), summarise, totSubjResp = sum(numSubjResp))
sumRespSubj <- merge(sumRespSubj, sumResp, by='subj')
sumRespSubj$pSubjResp <- with(sumRespSubj, numSubjResp/totSubjResp)
sumRespSE <- ddply(sumRespSubj, .(resp, ring), summarise,
                 seResp=sd(pSubjResp)/sqrt(length(subj)))
sumResp <- ddply(ds, .(resp, ring), summarise, numResp = length(subj))
sumResp$pResp <- sumResp$numResp / sum(sumResp$numResp)
sumResp <- merge(sumResp, sumRespSE, by=c('resp','ring'))
# write.table(sumResp,'clipboard',sep='\t',row.names=F, mode='r') #Windows
# write.table(sumResp,pipe('pbcopy'),sep='\t',row.names=F,col.names=F) #Mac
sumResp
```

## Slow
```{r}
sumSlowSubj <- ddply(ds, .(subj, vMin, vMax), summarise, 
                     pSubjResp = mean(slow))
sumSlow <- ddply(sumSlowSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumSlow$seResp[sumSlow$seResp==0] <- .02
sumSlow$seResp[is.na(sumSlow$seResp)] <- .02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlow, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Slow\nDominance\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4)) + ggtitle('a')
p <- themefy(p)
pSlow <- p
if(!out){plot(p)}else{png('mc_ct-v_slow2d2.png', width=3.2, height=2.1, units='in', res=600); plot(p); dev.off()}
```

### vMin (inset)
```{r, fig.height=3, fig.width=5}
pSlowIn <- ggplot(sumSlow[sumSlow$vMin==0,], aes(x=factor(vMax), y=pResp, 
                                                 group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,.5,1), labels=c('0','','1'), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank(), plot.background=element_rect(fill='grey'),
        axis.text.y = element_text(size=6))
```

## No-direction responses
```{r}
sumNoDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(noDir))
sumNoDir <- ddply(sumNoDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumNoDir$seResp[sumNoDir$seResp==0] <- .02
sumNoDir$seResp[is.na(sumNoDir$seResp)] <- .02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumNoDir, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='No-Direction\nResponses\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_noDir2d2.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Slow-direction
```{r}
sumSlowDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(slowDir))
sumSlowDir <- ddply(sumSlowDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumSlowDir$seResp[sumSlowDir$seResp==0] <- .02
sumSlowDir$seResp[is.na(sumSlowDir$seResp)] <- .02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlowDir, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Slow Direction\nResponses\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_slowDir2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Fast-direction
```{r}
sumFastDirSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(fastDir))
sumFastDir <- ddply(sumFastDirSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumFastDir$seResp[sumFastDir$seResp==0] <- .02
sumFastDir$seResp[is.na(sumFastDir$seResp)] <- .02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumFastDir, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Fast Direction\nResponses\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_fastDir2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Transparency
```{r}
sumTranspSubj <- ddply(ds, .(subj, vMin, vMax), summarise, pSubjResp = mean(transp))
sumTransp <- ddply(sumTranspSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumTransp$seResp[sumTransp$seResp==0] <- .02
sumTransp$seResp[is.na(sumTransp$seResp)] <- .02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumTransp, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + scale_colour_gradient(limits=c(0,1), breaks=c(0,.5,1)) +
    geom_point(data=sumSlow, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Patchy/\nTransparent\n(P trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_transp2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

# Slow-center/fast-surround
```{r}
sumRingSubj <- ddply(ds[ds$resp=='no direction',], .(subj, vMin, vMax), summarise,
                       pSubjResp = mean(ring), nSubjResp = sum(ring))
sumRing <- ddply(sumRingSubj, .(vMin, vMax), summarise,
                  pResp = mean(pSubjResp), 
                  nResp = mean(nSubjResp), 
                  seResp = sd(nSubjResp)/sqrt(length(subj)))
sumRing$seResp[which(is.na(sumRing$seResp))] <- .02
sumRing$seResp[which(sumRing$seResp==0)] <- .02
# sumRing$pResp[which(is.na(sumRing$seResp))] <- NA
```

## Frequency

### Number of center-surround
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMin), y=factor(vMax), color=nResp)) + 
    geom_point(size=4) + 
    scale_colour_gradient(limits=c(0,9), breaks=c(0,3,6,9)) + #, breaks=c(0,.5,1)) +
    geom_point(data=sumRing, shape=1, aes(x=factor(vMin), y=factor(vMax), size=9),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Center-\nSurround\n(N trials)\n') + 
    guides(color=guide_colorbar(barwidth=1, barheight=4)) + ggtitle('b')
p <- themefy(p)
pCS <- p
if(!out){plot(p)}else{png('mc_ct-v_ringV2d2n.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

### vMin (inset)
```{r, fig.height=3, fig.width=5}
pCSIn <- ggplot(sumRing[sumRing$vMin==0,], aes(x=factor(vMax), y=pResp, 
                                                 group=factor(vMin), 
                        ymin=pResp-seResp, ymax=pResp+seResp)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + 
    scale_y_continuous(breaks=c(0,.5,1), labels=c('0','','1'), limits=c(0,1)) + 
    theme_bw() + theme(panel.grid.minor.x=element_blank(), 
                       panel.grid.minor.y=element_blank(),
        axis.text.x = element_blank(), axis.title=element_blank(),
        legend.text = element_blank(), legend.title=element_blank(),
        legend.key = element_blank(), plot.background=element_rect(fill='grey'),
        axis.text.y = element_text(size=6))
```

### Proportion of center-surround
```{r, fig.height=3, fig.width=5}
p <- ggplot(sumRing, aes(x=factor(vMin), y=factor(vMax), color=pResp)) + 
    geom_point(size=4) + 
    geom_point(data=sumRing, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         color='Center/Surround\nTrials\n') 
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-v_ringV2d2p.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Center size: No-Direction
```{r}
sumRingSzPSubj <- ddply(ds[ds$resp=='no direction' & ds$ring==1,], .(subj, vMin, vMax), summarise,
                       ringSzPSubj = mean(ringSzP))
sumRingSzP <- ddply(sumRingSzPSubj, .(vMin, vMax), summarise,
                  ringSzP = mean(ringSzPSubj), 
                  ringSzPSe = sd(ringSzPSubj)/sqrt(length(subj)))
#sumRingSz$ringSzPSe[which(is.na(sumRingSzP$ringSzPSe))] <- 0
sumRingSzP$ringSzP[which(is.na(sumRingSzP$ringSzPSe))] <- NA
sumRingSzP$ringSzP[which(sumRingSzP$ringSzPSe==0)] <- NA
sumRingSzP$ringSzPSe[which(sumRingSzP$ringSzPSe==0)] <- NA
```

```{r, fig.height=3, fig.width=5}
sumRingSzPss <- sumRingSzP[!is.na(sumRingSzP$ringSzP),]
sumRingSzPss$vMin <- sumRingSzPss$vMin[,drop=T]
sumRingSzPss$vMax <- sumRingSzPss$vMax[,drop=T]
p <- ggplot(sumRingSzP, aes(x=factor(vMin), y=factor(vMax), size=ringSzP)) +
    geom_point(shape=3, color='grey', aes(x=factor(vMin), y=factor(vMax), size=ringSzPSe),
               show.legend=F) + geom_point(shape=1) + 
    geom_point(data=sumRingSzPss, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         size='Center Size')
p <- themefy(p)
p <- p + theme(panel.grid.major.x=element_blank(), panel.grid.major.y=element_blank())
if(!out){plot(p)}else{png('mc_ct-v_ringSz2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Center size: Slow
```{r}
sumRingSzPSubj <- ddply(ds[ds$slow==1 & ds$ring==1,], .(subj, vMin, vMax), summarise,
                       ringSzPSubj = mean(ringSzP))
sumRingSzP <- ddply(sumRingSzPSubj, .(vMin, vMax), summarise,
                  ringSzP = mean(ringSzPSubj), 
                  ringSzPSe = sd(ringSzPSubj)/sqrt(length(subj)))
#sumRingSz$ringSzPSe[which(is.na(sumRingSzP$ringSzPSe))] <- 0
sumRingSzP$ringSzP[which(is.na(sumRingSzP$ringSzPSe))] <- NA
sumRingSzP$ringSzP[which(sumRingSzP$ringSzPSe==0)] <- NA
sumRingSzP$ringSzPSe[which(sumRingSzP$ringSzPSe==0)] <- NA
```

```{r, fig.height=3, fig.width=5}
sumRingSzPss <- sumRingSzP[!is.na(sumRingSzP$ringSzP),]
sumRingSzPss$vMin <- sumRingSzPss$vMin[,drop=T]
sumRingSzPss$vMax <- sumRingSzPss$vMax[,drop=T]
p <- ggplot(sumRingSzP, aes(x=factor(vMin), y=factor(vMax), size=ringSzP)) +
    geom_point(shape=3, color='grey', aes(x=factor(vMin), y=factor(vMax), size=ringSzPSe),
               show.legend=F) + geom_point(shape=1) + 
    geom_point(data=sumRingSzPss, shape=1, aes(x=factor(vMin), y=factor(vMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         size='Center Size')
p <- themefy(p)
p <- p + theme(panel.grid.major.x=element_blank(), panel.grid.major.y=element_blank())
if(!out){plot(p)}else{png('mc_ct-v_slowRingSz2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

# Publication plots
```{r}
if(out){
    library(gridExtra)
    vp <- grid::viewport(x=.324, y=.373, width=.12, height=.3)
    vp2 <- grid::viewport(x=.8355, y=.373, width=.11, height=.3)
    jpeg('mc_ct-v_fig2.jpg', width=7, height=2.1, units='in', res=600)
    grid.arrange(pSlow, pCS, ncol=2, widths=c(2.55/5,2.45/5))
    print(pSlowIn, vp=vp)
    print(pCSIn, vp=vp2)
    dev.off()
}
```

# Analyses
```{r}
# Analysis
# library(lme4)
# library(BayesFactor)
#source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
```