---
title: "Motion clouds rivalry: Translational velocity"
author: "Egor Ananyev"
date: "April 14, 2017"
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data directories
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(reshape)
library(matrixStats)
#library(splines)
db <- '/home/egor/Dropbox/' # on Linux
db <- '/Users/Egor/Dropbox/' # Windows
#db <- '~/Dropbox/' # on Mac
# settings variables:
expt <- 'mcEcc_ct-bv'
subjs <- c(0:3)
sesss <- c(1:3)
# Read in the data directories:
dataDir <- paste(db, 'Projects/mc/data/', sep='')
condDir <- paste(dataDir,expt,'/', sep='')
allDirs <- dir(condDir)
```

## Plot variables
```{r}
# theme for plotting:
dodge <- position_dodge(width=0)
alpha <- 1 #.6
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=unit(-.04, 'in'),
            legend.background = element_rect(fill='transparent'))
}
cc <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f')
```

## Loading the data
```{r}
colsOfInt <- c('participant','session','trialN', #info
               'BvL','BvR', #IVs
               'nf000','nf090','nf180', 'nf270','ringSz') #DVs
df <- data.frame()
for(curSubj in subjs){
    for(curSess in sesss){
        grepPattern <- paste(expt, '_p', curSubj, '_s', curSess, sep='')
        sessDir <- allDirs[grep(grepPattern, allDirs)]
        print(sessDir)
        sessFn <- paste(condDir, sessDir, '/', sessDir, '.csv', sep='')
        if(file.exists(sessFn)){
            curDs <- read.csv(sessFn)
            df <- rbind(df, curDs[,colsOfInt])
        }
    }
}
head(df)
```

## Adjusting the data set
```{r}
# Selecting a subset of the data:
ds <- df
ds <- rename(ds, c(participant='subj', session='sess', BvL='bvL', BvR='bvR'))
# Measuring velocities in dps:
ds$bvR = round(ds$bvR*60/35,1)
ds$bvL = round(ds$bvL*60/35,1)
# The minimum size of the ring in the old paradigm corresponded to full field, so recoding:
ringSzMax=258
#ds$ringSz[ds$ringSz==25.8] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==0,'ringSz']) & ds$subj==0] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==1,'ringSz']) & ds$subj==1] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==2,'ringSz']) & ds$subj==2] <- ringSzMax
ds$ringSz[ds$ringSz==max(ds[ds$subj==3,'ringSz']) & ds$subj==3] <- ringSzMax
ds$ringSzDeg <- round(ds$ringSz/35,2)
ds$ringSzP <- round(ds$ringSz/258,2)
# The full-field should be coded as 'no center-surround', or 'no ring':
ds$ring <- 0
ds$ring[ds$ringSz!=ringSzMax] = 1
head(ds)
```

## Adding new columns
```{r}
# Creating columns for the slower and faster of the two speeds:
ds$bvMin <- rowMins(as.matrix(ds[c('bvL','bvR')]))
ds$bvMax <- rowMaxs(as.matrix(ds[c('bvL','bvR')]))
ds$bvDiff <- ds$bvMax - ds$bvMin
```

# Types of responses
```{r}
# noDir, fastDir, slowDir, transparent
ds$slow <- 0
ds$slow[ds$nf270==1] <- 1
ds$fast <- 0
ds$fast[ds$nf180==1] <- 1
ds$patchy <- 0
ds$patchy[ds$nf090==1] <- 1
ds$transp <- 0
ds$transp[ds$nf000==1] <- 1
ds$resp[ds$slow==1] <- 'slow'
ds$resp[ds$fast==1] <- 'fast'
ds$resp[ds$patchy==1] <- 'patchy'
ds$resp[ds$transp==1] <- 'transparent'
ds$resp <- factor(ds$resp, levels = c('slow','fast','patchy','transparent'))
head(ds)
```

## Slow
```{r}
sumSlowSubj <- ddply(ds, .(subj, bvMin, bvMax), summarise, pSubjResp=mean(slow),
                     nSubjResp=sum(slow))
sumSlow <- ddply(sumSlowSubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  nResp = mean(nSubjResp),
                  seResp = sd(nSubjResp)/sqrt(length(subj)))
sumSlow$seResp[which(is.na(sumSlow$seResp))] <- 0.02
sumSlow$seResp[which(sumSlow$seResp==0)] <- 0.02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlow, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=nResp)) + 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    geom_point(shape=3, color='lightgrey', aes(x=factor(bvMin), y=factor(bvMax), size=seResp),
               show.legend=F) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Slow Responses') +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_size(guide='none')
p <- themefy(p)
p <- p + theme(panel.grid.major.x=element_blank(), panel.grid.major.y=element_blank())
if(!out){plot(p)}else{png('mc_ct-bv_respSlow2d2.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Fast
```{r}
sumFastSubj <- ddply(ds, .(subj, bvMin, bvMax), summarise, pSubjResp = mean(fast))
sumFast <- ddply(sumFastSubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumFast$seResp[which(is.na(sumFast$seResp))] <- 0.02
sumFast$seResp[which(sumFast$seResp==0)] <- 0.02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumFast, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=I(1+.1/seResp))) + 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Fast Responses') +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-bv_respFast2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Transparent
```{r}
sumTranspSubj <- ddply(ds, .(subj, bvMin, bvMax), summarise, pSubjResp = mean(transp))
sumTransp <- ddply(sumTranspSubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
( ddply(ds, .(subj), summarise, pSubjResp=mean(transp), nSubjResp=sum(transp)) )
sumTransp$seResp[which(is.na(sumTransp$seResp))] <- 0.02
sumTransp$seResp[which(sumTransp$seResp==0)] <- 0.02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumTransp, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=I(1+.1/seResp))) + 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Transparency\nResponses') +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-bv_respTransp2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Patchy
```{r}
sumPatchySubj <- ddply(ds, .(subj, bvMin, bvMax), summarise, pSubjResp = mean(patchy))
sumPatchy <- ddply(sumPatchySubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumPatchy$seResp[which(is.na(sumPatchy$seResp))] <- 0.02
sumPatchy$seResp[which(sumPatchy$seResp==0)] <- 0.02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumPatchy, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=I(1+.1/seResp))) + 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Patchy\nResponses') +
    guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-bv_respPatchy2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```


# Center-surround
```{r}
( ddply(ds, .(subj, resp), summarise, pSubjResp = mean(ring), nSubjResp = sum(ring)) )
```

## Slow-center/fast-surround
```{r}
sumSlowRingSubj <- ddply(ds[ds$resp=='slow',], .(subj, bvMin, bvMax), summarise,
                       pSubjResp = mean(ring))
sumSlowRing <- ddply(sumSlowRingSubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
sumSlowRing$seResp[which(is.na(sumSlowRing$seResp))] <- 0.02
sumSlowRing$seResp[which(sumSlowRing$seResp==0)] <- 0.02
# sumSlowRing$pResp[which(is.na(sumSlowRing$seResp))] <- NA
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumSlowRing, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=I(1+.1/seResp)))+ 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Slow-Center/\nFast-Surround') + 
    guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-bv_ringSlow2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

## Fast-center/slow-surround
```{r}
sumFastRingSubj <- ddply(ds[ds$resp=='fast',], .(subj, bvMin, bvMax), summarise,
                       pSubjResp = mean(ring))
sumFastRing <- ddply(sumFastRingSubj, .(bvMin, bvMax), summarise,
                  pResp = mean(pSubjResp), 
                  seResp = sd(pSubjResp)/sqrt(length(subj)))
#sumFastRing$pResp[which(is.na(sumFastRing$seResp))] <- 0
#sumFastRing$seResp[which(is.na(sumFastRing$seResp))] <- 0
sumFastRing$seResp[which(is.na(sumFastRing$seResp))] <- 0.02
sumFastRing$seResp[which(sumFastRing$seResp==0)] <- 0.02
```

```{r, fig.height=3, fig.width=5}
p <- ggplot(sumFastRing, aes(x=factor(bvMin), y=factor(bvMax), colour=pResp, size=I(1+.1/seResp)))+ 
    geom_point() + scale_colour_gradient(low='green', high='red', limits=c(0,1)) +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         colour='Fast-Center/\nSlow-Surround') + 
    guides(colour=guide_legend(keyheight=.2, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('mc_ct-bv_ringFast2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

# Center size: Proportion of ring size

## Slow
```{r}
sumRingSzPSubj <- ddply(ds[ds$resp=='slow' & ds$ring==1,], .(subj, bvMin, bvMax), summarise,
                       ringSzPSubj = mean(ringSzP))
sumRingSzP <- ddply(sumRingSzPSubj, .(bvMin, bvMax), summarise,
                  ringSzP = mean(ringSzPSubj), 
                  ringSzPSe = sd(ringSzPSubj)/sqrt(length(subj)))
#sumRingSz$ringSzPSe[which(is.na(sumRingSzP$ringSzPSe))] <- 0
# sumRingSzP$ringSzP[which(is.na(sumRingSzP$ringSzPSe))] <- NA
# sumRingSzP$ringSzP[which(sumRingSzP$ringSzPSe==0)] <- NA
sumRingSzP$ringSzPSe[which(sumRingSzP$ringSzPSe==0)] <- 0.02
sumRingSzP$ringSzPSe[which(is.na(sumRingSzP$ringSzPSe))] <- 0.02
```

```{r, fig.height=3, fig.width=5}
sumRingSzPss <- sumRingSzP[!is.na(sumRingSzP$ringSzP),]
sumRingSzPss$vMin <- sumRingSzPss$bvMin[,drop=T]
sumRingSzPss$vMax <- sumRingSzPss$bvMax[,drop=T]
p <- ggplot(sumRingSzP, aes(x=factor(bvMin), y=factor(bvMax), size=ringSzP)) +
    geom_point(shape=3, color='grey', aes(x=factor(bvMin), y=factor(bvMax), size=ringSzPSe),
               show.legend=F) +
    geom_point(shape=1) + 
    geom_point(data=sumRingSzPss, shape=1, aes(x=factor(bvMin), y=factor(bvMax), size=1),
               show.legend=F, color ='lightgrey') +
    labs(x=expression(paste('Lower Speed (', degree, '/s)', sep='')), 
         y=expression(paste('Higher Speed (', degree, '/s)', sep='')), 
         size='Center Size')
p <- themefy(p)
p <- p + theme(panel.grid.major.x=element_blank(), panel.grid.major.y=element_blank())
if(!out){plot(p)}else{png('mc_ct-bv_ringSz2d.png', width=3.2, height=1.9, units='in', res=600); plot(p); dev.off()}
```

# Analyses
```{r}
# Analysis
#library(lme4)
#library(lmerTest)
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
```